%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvpubsection{Publications List}


\cvpubsubsection{Peer-reviewed Journal Articles}
\hspace{\smallsephintwidth}$\dagger$ - I was a co-first-author on this paper \\
\hspace{\smallsephintwidth}$*$ - This paper was led by someone I mentor
\vspace{0.3cm}

\cvpub{2022}
	  {17}
	  {
		Jermyn, A.S.; \textbf{Anders, E.H.}; Lecoanet, D.; and Cantiello, M. Accepted for publication in ApJS.
        \href{https://arxiv.org/abs/2206.00011}{(ArXiv).}
       }
	  {An Atlas of Convection in Main Sequence Stars.}

\cvpub{}
      {$^*$16}
      {
        Fuentes, J.R.; Cumming, A.; \textbf{Anders, E.H.}. Submitted to PRF.
        \href{https://arxiv.org/abs/2204.12643}{(ArXiv).}
      }
      {Layer formation in a stably-stratified fluid cooled from above. Towards an analog for Jupiter and other gas giants.}

\cvpub{}
      {$^\dagger$15}
      {
        Fraser, A.E.; Joyce, M.; \textbf{Anders, E.H.}; Tayar, J.; Cantiello, M. submitted to ApJ.
        \href{https://arxiv.org/abs/2204.08487}{(ArXiv).}
      }
      {Observed Extra Mixing Trends in Red Giants are Reproduced by the Reduced Density Ratio in Thermohaline Zones.}

\cvpub{}
	  {14}
	  {
		Jermyn, A.S.; \textbf{Anders, E.H.}; Lecoanet, D.; and Cantiello, M. 
        \href{https://iopscience.iop.org/article/10.3847/1538-4357/ac5f08}{ApJ 929, 182.}
	  }
	  {Convective Penetration in Early-Type Stars}

\cvpub{}
	  {13}
	  {
		\textbf{Anders, E.H.}; Jermyn, A.S.; Lecoanet, D.; Fraser, A.E.; Cresswell, I.G.; Joyce, M.; and Fuentes, J.R. 
        \href{https://iopscience.iop.org/article/10.3847/2041-8213/ac5cb5}{ApJL 928, L10}.
	  }
	  {Schwarzschild and Ledoux are equivalent on evolutionary timescales}

\cvpub{}
	  {12}
	  {
		Jermyn, A.S.; \textbf{Anders, E.H.}; and Cantiello, M. 
        \href{https://iopscience.iop.org/article/10.3847/1538-4357/ac4e89}{ApJ 926, 221}.
	  }
	  {A Transparent Window into Early-Type Stellar Variability}

\cvpub{}
	  {11}
	  {
		\textbf{Anders, E.H.}; Jermyn, A.S.; Lecoanet, D.; and Brown, B.P., 
        \href{https://iopscience.iop.org/article/10.3847/1538-4357/ac408d}{ApJ 926, 169}.
	  }
	  {Stellar convective penetration: parameterized theory and dynamical simulations}

\cvpub{2021}
	  {$^*$10}
	  {
		O'Connor, L.; Lecoanet, D.; and \textbf{Anders, E.H.}, 
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.6.093501}{Physical Review Fluids 6, 093501.}
	  }
	  {Marginally-Stable Thermal Equilibria of Rayleigh-B\'{e}nard Convection}

\cvpub{}
	  {9}
	  {
		Lecoanet, D.; Cantiello, M.; \textbf{Anders, E.H.}; Quataert, E.; Couston, L.; Bouffard, M.; Favier, B.; and Le Bars, M.,
          \href{https://doi.org/10.1093/mnras/stab2524}{MNRAS 508, 1, 132-143.}
	  }
	  {Surface Manifestation of Stochastically Excited Internal Gravity Waves}

\cvpub{}
	  {8}
	  {
		 Van Kooten, S.J.; \textbf{Anders, E.H.}; and Cranmer, S.R,
		  \href{https://iopscience.iop.org/article/10.3847/1538-4357/abf7bf}{ApJ 913, 69}
	  }
	  {A Refined Model of Convectively-Driven Flicker in Kepler Light Curves}

\cvpub{}
	  {7}
	  {
		Oishi, J.S.; Burns, K.J.; Clark, S.E.; \textbf{Anders, E.H.}; Brown, B.P.; Vasil, G.M.; and Lecoanet, D,
		  \href{https://joss.theoj.org/papers/10.21105/joss.03079}{JOSS 6(62), 3079}.
	  }
	  {eigentools: A Python package for studying eigenvalueproblems with an emphasis on stability}

\cvpub{2020}
	  {6}
	  {
		  \textbf{Anders, E.H.}; Vasil, G.M.; Brown, B.P.; and Korre, Lydia, 
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.5.083501}{Physical Review Fluids 5, 083501.}
	  }
	  {Convective dynamics with mixed temperature boundary conditions: why thermal relaxation matters and how to accelerate it}

\cvpub{2019}
	  {5}
	  {
		  \textbf{Anders, E.H.}; Lecoanet, D.; and Brown, B.P., 
		  \href{https://iopscience.iop.org/article/10.3847/1538-4357/ab3644}{ApJ 884, 65.}
	  }
	  {Entropy Rain: Dilution and Compression of Thermals in Stratified Domains}

\cvpub{}
	  {4}
	  {
		  \textbf{Anders, E.H.}; Manduca, C.M.; Brown, B.P.; Oishi, J.S.; Vasil, G.M., 
		  \href{https://iopscience.iop.org/article/10.3847/1538-4357/aaff61}{ApJ 872, 2.}
	  }
	  {Predicting the Rossby Number in Convective Experiments}

\cvpub{2018}
	  {3}
	  {
		  \textbf{Anders, E.H.}; Brown, B.P; and Oishi, J. S.,
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.3.083502}{Physical Review Fluids 3, 083502.}
	  }
	  {Accelerated evolution of convective simulations}

\cvpub{2017}
	  {2}
	  {
		  \textbf{Anders, E.H.} and Brown, B.P.,
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.2.083501}{Physical Review Fluids 2, 083501.}
	  }
	  {Convective heat transport in stratified atmospheres at low and high Mach number}

\cvpub{2016}
	  {1}
	  {
			Karki, S.; Tuyenbayev, D.; Kandhasamy, S.; Abbott, B.P.; Abbott, T.D.; \textbf{Anders, E.H.};
			Berliner, J.; Betzwieser, J.; Cahillane, C.; Canete, L.; Conley, C.; Daveloza, H.P.; De Lillo, N.;
			Gleason, J.R.; Goetz, E.; Izumi, K.; Kissel, J.S.; Mendell, G.; Quetschke, V; Rodruck, M.; Sachdev, S.;
			Sadecki, T.; Schwinberg, P.B.; Sottile, A.; Wade, M.; Weinstein, A.J., West, M.; and Savage, R.L.,
			\href{https://aip.scitation.org/doi/10.1063/1.4967303}{Review of Scientific Instruments 87, 114503.}
	  }
	  {The Advanced LIGO photon calibrators}


\cvpubsubsection{Other Publications}
\cvpub{2022}
	  {3}
	  {
		\textbf{Anders, E.H.}; Bauer, E.B.; Jermyn, A.S.; Van Kooten, S.J.; Brown, B.P.; Hester, E.W.; Wilkinson, M.; Goldberg, J.A.; Varesano, T.; Lecoanet, D.
        \href{https://arxiv.org/abs/2204.00002}{ArXiv; April fool's paper.}
	  }
	  {Moosinesq Convection in the Cores of Moosive Stars}

\cvpub{2022}
	  {2}
	  {
		\textbf{Anders, E.H.}; Jermyn, A.S.; Lecoanet, D.; Fuentes, J.R.; Korre, L.; Brown, B.P.; Oishi, J.S.; 
        \href{https://iopscience.iop.org/article/10.3847/2515-5172/ac5892}{RNAAS 6, 41.}
	  }
	  {Convective Boundary Mixing Processes}

\cvpub{}
	  {1}
	  {
		Jermyn, A.S.; \textbf{Anders, E.H.}; Lecoanet, D.; Cantiello, M.; and Goldberg, J.A.; 
        \href{https://iopscience.iop.org/article/10.3847/2515-5172/ac531e}{RNAAS 6, 29.}
	  }
	  {Measures of Convective Efficiency}


