\documentclass[12pt,pdf]{letter}

\usepackage{hyperref}

\input{./myletter}                         
                         
\begin{document}

\address{\ \\ \  \\ \\ \\ \\ \\ \\ \\
Chair \\
Committee on Hiring \\
Engineering Sciences and Applied Mathematics \\
Northwestern University.
}

\opening{Dear Committee:}

I am applying for the position of Assistant Professor in Applied Mathematics at the Northwestern University Department of Engineering Sciences and Applied Mathematics.  With this letter, please find my curriculum vitae, research and teaching statements, and four selected publications.

My work centers on Astrophysical and Geophysical Fluid Dynamics (AGFD).  I combine analytic calculations, simulations, and experiments to build and test models of basic fluid processes in AGFD.  I develop the simplest possible model which includes the important physical mechanisms for a given astrophysical or geophysical phenomenon.  My goal in analyzing such models is to gain physical intuition regarding the phenomenon of interest.

Since visiting Northwestern last year, I have mostly worked in two areas. First, I have run and analyzed a set of simulations of thermals, which study the release of a finite volume of buoyant fluid. The results have recently been submitted to {\it JAS} (and is included in this application). Over the past year, my collaborator on this project, Nadir Jeevanjee (GFDL), \& I have supervised two undergraduate students, who have further analyzed these simulations to test theories of effective buoyancy, turbulent drag, and laminar entrainment. This has resulted in one paper published in {\it JAS}, and another paper currently under preparation. I also recently spent three weeks at IRPHE in Marseille, France, doing experiments of thermals in new regimes which aid quantitative comparison to simulations.

My other main focus has been extending the Dedalus PDE framework to solve PDEs in different geometries which have coordinate singularities. In particular, we have run forced turbulence simulations in a 2D disk; simulations of a generalized Navier--Stokes equation on the 2D surface of a sphere, as a model for active matter; and a series of 3D benchmark convection and dynamo problems in a full ball. The latter is the subject of two papers together with my collaborator Geoffrey Vasil, which are currently under review at {\it JCP} (one is included in this application). For each of these geometries, we have developed numerical methods for solving nearly arbitrary tensorial equations. This is a major advance over previous work which always required the equations to be written in terms of scalar quantities.

My research program is synergistic with the Applied Mathematics Department. Dedalus is a promising tool for a wide range of problems of interest to the Department, including pattern formation (Alvin Bayliss), nonlinear optimization (William Kath), bubble dynamics (Petia Vlahovska), and more. I am interested in numerical strategies for multiphase dynamics and melting/solidification, and look forward to discussing these with David Chopp. I would be excited to join a department with so many people interested in different aspects and applications of fluid dynamics. More broadly, my work has natural connections to others studying AGFD at Northwestern, in particular Yoram Lithwick (Physics \& Astronomy) and Seth Jacobson (Earth \& Planetary Sciences).

I believe I will make outstanding research, teaching, and service contributions to the Department of Engineering Sciences and Applied Mathematics.  In support of my application, please feel free to contact the following individuals:

\vspace{2mm}

\begin{tabular}{lll}
Prof.  Eliot Quataret
&\hspace{4mm} &
Prof. Rich Kerswell
\\
Department of Astronomy,
&\hspace{1mm}  &
DAMTP, 
\\
University of California -- Berkeley
&\hspace{1mm}  &
University of Cambridge
\\
501 Campbell Hall \#3411 
&\hspace{1mm}  &
Centre for Mathematical Sciences
\\
Berkeley, CA 94720
&\hspace{1mm}  &
Cambridge CB3 0WA, U.K. 
\\
Tel: (510) 642-3792
&\hspace{1mm}  &
Tel: +44 1223 766349
\\
eliot@berkeley.edu
&\hspace{1mm}  &
R.R.Kerswell@damtp.cam.ac.uk 
\\
\
&\hspace{1mm}  &
%zweibel@astro.wsic.edu
\\[0mm] 
Dr. Michael Le Bars
&\hspace{4mm} &
\\
IRPHE
&\hspace{1mm}  &
\\
49, Rue F. Joliot-Curie - B.P. 146 
&\hspace{1mm}  &
\\
13384 Marseille Cedex 13 
&\hspace{1mm}  &
\\
France
&\hspace{1mm}  &
\\
Tel. +33 4 13 55 20 73
&\hspace{1mm}  &
\\
lebars@irphe.univ-mrs.fr
&\hspace{1mm}  & 
\end{tabular}

If there are any other questions or concerns please do not hesitate to contact me. Thank you for your time and consideration.
\vspace{-2mm}
\closing{Best Regards,}
\signature

\end{document}
